Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-06-12 ICPP-19/DataTransferModels/dataTransferModels.tex
ICPP-19 submitted files

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
%%\acmPrice{15.00}
%%\acmDOI{10.1145/1122445.1122456}
%%\acmISBN{978-1-4503-9999-9/18/06}

@@

		%
		% The next two lines define the bibliography style to be used, and the bibliography file.
		\bibliographystyle{ACM-Reference-Format}
		\bibliography{communications}

>>>>

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{licensedusgovmixed}
\acmConference[ICPP 2019]{48th International Conference on Parallel Processing}{August 5--8, 2019}{Kyoto, Japan}
\acmBooktitle{48th International Conference on Parallel Processing (ICPP 2019), August 5--8, 2019, Kyoto, Japan}
\acmPrice{15.00}
\acmDOI{10.1145/3337821.3337921}
\acmISBN{978-1-4503-6295-5/19/08}

@@

		%
		% The next two lines define the bibliography style to be used, and the bibliography file.
		\bibliographystyle{ACM-Reference-Format}
		\bibliography{dataTransferModels}

### 2019-06-12 ICPP-19/communications.tex
ICPP-19 submitted files

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
%%\acmPrice{15.00}
%%\acmDOI{10.1145/1122445.1122456}
%%\acmISBN{978-1-4503-9999-9/18/06}

>>>>

%%\copyrightyear{2019}
%%\acmYear{2019}
%%\setcopyright{acmlicensed}
%%\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
%%%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
%%%%\acmPrice{15.00}
%%%%\acmDOI{10.1145/1122445.1122456}
%%%%\acmISBN{978-1-4503-9999-9/18/06}

\copyrightyear{2019}
\acmYear{2019}
%%\setcopyright{acmlicensed}
%%\setcopyright{llicensedusgovmixed}
\setcopyright{licensedusgovmixed}

%%none,%
%%acmcopyright,acmlicensed,rightsretained,%
%%usgov,usgovmixed,cagov,cagovmixed,licensedusgovmixed,%
%%licensedcagov,licensedcagovmixed,othergov,licensedothergov,%
%%iw3c2w3,iw3c2w3g

\acmConference[ICPP 2019]{48th International Conference on Parallel Processing}{August 5--8, 2019}{Kyoto, Japan}
\acmBooktitle{48th International Conference on Parallel Processing (ICPP 2019), August 5--8, 2019, Kyoto, Japan}
\acmPrice{15.00}
\acmDOI{10.1145/3337821.3337921}
\acmISBN{978-1-4503-6295-5/19/08}
